Simulating Ultra High-Dimensional Multivariate Data Using the bigsimr R Package

### 2020-10-21 index.Rmd
move brca99.rds creation to index.Rmd

>>>>

```{r processBRCA, echo=FALSE, eval=TRUE, results='none'}
if ( !file.exists( 'data/brca99.rds' ) )  {
    ## full workflow simulating RNA-seq data
    allDat <- readRDS( file = "~/Downloads/complete_processed_tcga2stat_RNASeq2_with_clinical.rds" )
    lastClinical <- which( names(allDat) == 'tumorsize' )
    brca <- allDat[ allDat$disease == "BRCA", (lastClinical+1):ncol(allDat) ]
    dim(brca) ## num of genes 20501
    ## compute the median expression! avoid the 0s
    brcaMedian <- apply(brca, 2, median)
    ## retain top (1-probs)*100% highest expressing genes for illustration
    myProb <- 0.99
    cutPoint <- quantile( x = brcaMedian, probs = myProb )
    ## genesToKeep <- names( brcaMedian ) [ which(brcaMedian >= cutPoint) ]
    genesToKeep <- names( brcaMedian ) [ which(brcaMedian >= cutPoint) ]
    brca <- brca[ , genesToKeep ]
    ## ncol(brca) / 20501
    print(d <- length(genesToKeep))
    ## save data as rds
    saveRDS(brca, 'data/brca99.rds')
}
```
